\bf $\mathsf{BATE}$: Boosting Bandwidth Availability Over Inter-DC WAN

### 2021-01-24 paper.tex
testbed description

\section{Evaluation} \label{evaluation}
In this section, we evaluate the performance of $\mathsf{BATE}$  in both real trace driven simulation and testbed.
Our main results are as follows.

%We begin by describing the experimental framework ($\S$ \ref{setting}). 
%We show the performance of $\mathsf{BATE}$ through answering the following specific questions:
(1)  The admission control of $\mathsf{BATE}$ can achieve a reasonable tradeoff. $\mathsf{BATE}$ can speed up the online admission control by 30 $\times$ at the expense of 5\% higher rejection ratio.

%compared with the latest TE schemes like FFC and TEAVAR, BATE can meet the availability SLAs of 40% more bandwidth demands, and when network failure causes SLA violations, it can retain 30% more profit under a simple pricing and refunding model.
(2) $\mathsf{BATE}$ has consistent performance under various topologies and traffic.
Compared with the state-of-the-art traffic engineering algorithms, $\mathsf{BATE}$ is able to make  40\% more bandwidth demands meet availability SLAs.

(3) $\mathsf{BATE}$ can retain 30\% more profit when network fails.

(4)  $\mathsf{BATE}$ is fast and accuracy.
The average error of traffic scheduling is within 8\% and the profit loss of greedy algorithm is less than 10\%.

@@

\subsection{Testbed evaluation}\label{testbed-evaluation}
\subsubsection{Testbed setup}
We build a small testbed with 6 servers to emulate an inter-DC WAN with 6 DCs as in Figure \ref{testbed}.
Each server equips with 4 Intel Xeon E5-2620 CPUs, 64GB memory and 4 Ethernet NICs, and runs Centos 7 64-bit version with Linux 4.15.6 kernel \cite{Kermel}.
Each inter-DC WAN link is emulated using 1Gbps physical link.
We use 4-shortest path to decide tunnel set of each node pair.
Controller locates in DC1 and runs the software defined networking framework.
We add 100ms delay to emulate the WAN environment.
We start 21 VMs (1 vCPU, 2GB memory, 100GB disk) in each server, where 20 VMs are used to emulate the hosts and 1 VM runs as the broker.
Each VM belongs to only one customer and will send  \textit{iperf} UDP flows with specified rates to other DCs.
%Each VM has a demand and the it varies with a period of 3-minutes pattern just as \cite{swan}.  
%The importance of services are randomly chosen from \{1,2,3,4,5\} 
%All services have the same level of importance and availability targets of services are from the SLAs of Azure \cite{azure}.
The network agent in broker runs Floodlight \cite{floodlight} as the OpenFlow controller.
In each data center, all hosts and  NICs connect to an Open vSwitch \cite{openvswitch}.
We start an extra VM in DC1 as the controller. 
%CPU, memory and disk are not the bottleneck in our experiments.
All switches run link liveness detection protocol, and they report any failures to brokers.
Every second, we randomly generate an integer $p$ between 0 and 10000 for each link.
If  $p/10000$ is smaller than the failure threshold shown in Figure \ref{testbed}, we disable the network interface to emulate link failure.
Then after 3 seconds, we enable the network interface to emulate link repair.
We also evaluate FFC \cite{FFC} and TEAVAR \cite{Teavar} to make comparisons.
%We mainly care about the following metrics:
%(1) Availability.  Bandwidth-based availability is measured as the time qualification ratio. A second is regarded as qualified if the gap between total measured bandwidth and bandwidth demand is less than 1\%;
%(2) Data loss ratio. We measure total bytes loss according to \textit{iperf} server side reports and packet counters in the switches, then finally derive the data loss ratio;
%(3) Demand rejection ration of different admission control algorithms;
%(4) Profit loss after link failures.
%The achieved  availability is computed as the fraction of qualified seconds, where . 
%We perform the experiment for a duration of 100 minutes.
%We deploy 5 applications and each instance will send traffic to other VMs located in the rest DCs.
%The importance of applications are randomly chosen from \{1,2,3,4,5\} with poisson distribution.
% Availability target of applications are randomly chosen from \{90\%, 95\%, 99\%, 99.9\%, 99.99\%\} with uniform distribution.

@@

\section{Proof of NP-hardness} \label{appendix1}

>>>>

\section{Evaluation} \label{evaluation}
In this section, we use a small testbed and larger scale trace driven simulations  to evaluate the performance of $\mathsf{BATE}$. 
On the testbed, we also implement two TE algorithms, i.e., FFC \cite{FFC} and TEAVAR \cite{Teavar}. 
For simulation, we implement more algorithms, including xxx. 
All codes for our implementation and evaluation will be published, 
so that interested readers can use them in other environments or make further improvements.

Our main results are as follows:

%We begin by describing the experimental framework ($\S$ \ref{setting}). 
%We show the performance of $\mathsf{BATE}$ through answering the following specific questions:
%compared with the latest TE schemes like FFC and TEAVAR, BATE can meet the availability SLAs of 40% more bandwidth demands, and when network failure causes SLA violations, it can retain 30% more profit under a simple pricing and refunding model.
(1) $\mathsf{BATE}$ consistently ourperforms latests TE algorithms under various topologies, traffic matrices and failure scenarios. With $\mathsf{BATE}$, up to 40\% more bandwidth availability demands can be successfully fulfilled, and 30\% more profit can be retained when failures occur.

(2) $\mathsf{BATE}$ achieves a good tradeoff between efficiency and optimality. 
Compared with the optimal solutions, (i) our admission control algorithm can speed up the admission procedure by 30$\times$ at the expense of only 5\% higher rejection ratio, 
(ii) our pruning-augmented scheduling algorithm runs xx$\times$ faster with only 6\% waste of total bandwidth and 8\% loss in the overall availability, 
and (iii) our greedy failure recovery algorithm needs xx$\times$ less time to react, 
where the achieved profit decreases by less than 10\%.

@@

\subsection{Testbed evaluation}\label{testbed-evaluation}
\textbf{Testbed setup}
We build a small testbed with 6 servers to emulate an inter-DC WAN connecting 6 DCs, as shown in Figure \ref{testbed}. 
The inter-DC links run at 1Gbps, and we add 100ms delay on each link to emulate a WAN environment.
Each server is equipped with 4 Intel Xeon E5-2620 CPUs, 64GB memory and 4 Ethernet NICs, 
and on each server we start 20 VMs, which are all connected to an Open vSwitch \cite{openvswitch}.
The VMs run CentOS 7 and use Linux v4.15.6 kernel \cite{Kermel} with our rate limiting module plugged in. 
%We start 21 VMs (1 vCPU, 2GB memory, 100GB disk) in each server, where 20 VMs are used to emulate the hosts and 1 VM runs as the broker.
Every second, we emulate link failures by shutting down the corresponding VM interfaces 
under the failure probabilities shown in Fig. \ref{testbed}, 
and bring them online after 3 seconds. 
We also deploy our controller and brokers on extra VMs. 
The network agent module in each broker uses Floodlight \cite{floodlight} to control the vSwitch, 
while the latter monitors link status and reports any failure to the former.
If not stated otherwise, we use 4 shortest paths between each source-destination pair as the tunnels in TE algorithms.

%Each VM has a demand and the it varies with a period of 3-minutes pattern just as \cite{swan}.  
%The importance of services are randomly chosen from \{1,2,3,4,5\} 
%All services have the same level of importance and availability targets of services are from the SLAs of Azure \cite{azure}.

%We mainly care about the following metrics:
%(1) Availability.  Bandwidth-based availability is measured as the time qualification ratio. A second is regarded as qualified if the gap between total measured bandwidth and bandwidth demand is less than 1\%;
%(2) Data loss ratio. We measure total bytes loss according to \textit{iperf} server side reports and packet counters in the switches, then finally derive the data loss ratio;
%(3) Demand rejection ration of different admission control algorithms;
%(4) Profit loss after link failures.
%The achieved  availability is computed as the fraction of qualified seconds, where . 
%We perform the experiment for a duration of 100 minutes.
%We deploy 5 applications and each instance will send traffic to other VMs located in the rest DCs.
%The importance of applications are randomly chosen from \{1,2,3,4,5\} with poisson distribution.
% Availability target of applications are randomly chosen from \{90\%, 95\%, 99\%, 99.9\%, 99.99\%\} with uniform distribution.

@@

\section{Proof of NP-hardness in Failure Recovery} \label{appendix1}
